Viscous Transport in Eroding Porous Media

### 2019-05-02 docs/transport/erosion_transport.tex
correct an error in tranposrt paper
doing tranposrt paper

\xx=x_1+x_2, \,\,

@@

\frac{\partial v_1(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 

@@

\frac{\partial v_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 

@@

      +x_2\operatorname{Im} (v''[\eta_2](x)).

@@

Since we are able to write on all our quantities of interest in terms of
a Cauchy integral and its derivatives, we only require a near-singular
integration method for equation~\eqref{eqn:Cauchy}.  A quadrature scheme
for $v(x)$, for a target point $x$, is
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^N 
    w_j \frac{\tau(y_j)}{x - y_j},
\end{align}
where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
quadrature nodes.  If the trapezoid rule is used, the quadrature rule
has spectral accuracy.  However, for a fixed resolution $N$, the error
grows without bound as $x$ approaches $\Gamma$.  As outline by Barnett
et al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
Barycentric quadrature rule
\begin{align}
  v(x) \approx \frac{\sum_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
  v'(x) \approx \frac{\sum_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum_{j=1}^N \frac{1}{y_j-x}w_j}, 
\end{align}
is used, where $x$ is a target point that is interior to $\Gamma$,
and $v_j^-$ is the value of $v(y_j)$.  Modifications of this formula
exist if $x$ is exterior to $\Gamma$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barcyentric Quadrature for $v''(x)$}
In order to simulate erosion, we require the deformation gradient which
means that a quadrature rule for $v''(x)$ is required.  Using the same
techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
quadrature rule for the second derivative can be constructed using the
identities
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{v^-(y)-v(x)}{y-x} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.
\end{alignat}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation Methods}
\label{sec:fmm}
\begin{itemize}
  \item Apply trapezoid rule as a first pass
  \item Efficiently find points that are too close for trapezoid
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly
\end{itemize}

>>>>

\xx=(x_1,x_2), \,\,

@@

\frac{\partial u_2(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 

@@

\frac{\partial u_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 

@@

      +x_2\Re (v''[\eta_2](x)).

@@

Since we are able to write on all our quantities of interest in terms of
a Cauchy integral and its derivatives, we only require a near-singular
integration method for equation~\eqref{eqn:Cauchy}.  A quadrature scheme
for $v(x)$, for a target point $x$, is
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^N 
    w_j \frac{\tau(y_j)}{x - y_j},
\end{align}
where $w_j$ are the quadrature weights and $y_j \in \Gamma$ are the
quadrature nodes.  If the trapezoid rule is used, the quadrature rule
has spectral accuracy.  However, for a fixed resolution $N$, the error
grows without bound as $x$ approaches $\Gamma$.  As outline by Barnett
et al.~\cite{bar-wu-vee2015}, the error is uniformly bounded if the
Barycentric quadrature rule
\begin{align}
  v(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^-}{y_j-x}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j},  \qquad
  v'(x) \approx \frac{\sum\limits_{j=1}^N \frac{v_j^- - v(x)}{(y_j - x)^2}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, 
\end{align}
is used, where $x$ is a target point that is interior to $\Gamma$,
and $v_j^-$ is the value of $v(y_j)$.  Modifications of this formula
exist if $x$ is exterior to $\Gamma$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barcyentric Quadrature for $v''(x)$}
In order to simulate erosion, we require the deformation gradient which
means that a quadrature rule for $v''(x)$ is required.  Using the same
techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
quadrature rule for the second derivative can be constructed using the
identities
{\color{red}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3}, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation Methods}
\label{sec:fmm}
\begin{itemize}
  \item Apply trapezoid rule as a first pass
  \item Efficiently find points that are too close for trapezoid

{\color{red}
To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points. Let $L_w$ be the length of the boundary of wall and $L_{b}$ be length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of wall to body,  let $d$ be the minimum distance between wall to a point $x_i$ on the body $b$, we define they are too close when
$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the minimum distance between a point $y_j$ on the body $b_1$ to a point $x_i$ on the body $b_2$, we define they are too close when
$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_1}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
where $\alpha_2$ is a constant.

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly
\end{itemize}
